---
title: "Introduction to the crosstab function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro_Crosstab}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
library(qacr)
```

The **crosstab** function calculates and prints a two-way frequency table. 

Given a data frame, a row variable, a column variable, and a type (frequencies, cell percents, row percents, or column percents) the function returns a table with

* labeled rows and columns   
* frequencies or percents   
* a level labeled \<NA\> for missing values (unless `na.rm = TRUE`)   
* a level labeled Total (unless `total = FALSE`)

Tables are printed with 2 decimal places for percents (modifiable using `digits=#`). Variables are coerced to factors if necessary.

Here are some examples.

### Frequencies

```{r}
crosstab(mtcars, cyl, gear)
```

### Row percents

```{r}
crosstab(mtcars, cyl, gear, type = "rowpercent")
```

### Column percents

```{r}
crosstab(mtcars, cyl, gear, type = "colpercent")
```

### Saving the results
You can save the results as a table.

```{r}
result <- crosstab(mtcars, cyl, gear)
result$tbl
result$cellPcts
result$rowPcts
result$colPcts

```
