---
title: "Introduction to the dstats function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro_dstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo=TRUE, eval=TRUE, error=FALSE, warning=FALSE, message=FALSE}
library(qacr)
```


This function provides descriptive statistics for a quantitative variable (unquoted). If no keyword arguments for statistics are provided, default values are used. Default stats: c("n", "mean", "sd")
```{r include=TRUE}
dstats(oil,operator)
```

You supply statistics argument with the "stats" parameter. You can pass single statistic or multiple statistics as a list object.
Singe statistic:
```{r include=TRUE}
dstats(oil,operator, stats = c("median"))
```

Multiple statistics:
```{r include=TRUE}
dstats(soils, pH, stats = c("median", "mean", "sd"))
```


You can supply as many grouping variables as needed. 
```{r include=TRUE}
dstats(soils, pH, Group, Contour, Depth)
```



You can pass multiple statistics and multiple grouping variable at the same time.
```{r include=TRUE}
dstats(soils, pH, Group, Contour, stats=c("mean", "median", "sd"))
```


User-defined functions can also be used as the 'statistic'. It's passed using the statistic parameter:
```{r include=TRUE}
#custom statistic
my_n <- function(xs) length(xs)

#calling the custom statistic
dstats(soils, pH, stats = c("my_n"))
```


User-defined functioned can also be passed alongside other statistics:
```{r include=TRUE}
dstats(soils, pH, Group, Contour, Depth, stats=c("my_n","mean"))
```


Other optionalinputs into the function include the 'na.rm' parameter. When TRUE, NAs are removed. Default is TRUE
```{r include=TRUE}
dstats(soils, pH, Depth, stats=c("mean","median","sd"),  na.rm=FALSE)
```


Another optional input is digit, which is the number of decimal points to print. Default = 2. 
```{r include=TRUE}
dstats(soils, pH, Depth, stats=c("mean","median","sd"), na.rm=FALSE, digits=3)
```
























