---
title: "Introduction to the tab function"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{tab_vingette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(qacr)

```

The tab function provides a frequency table for a categorical variable. Many options are available.

The **venues** data frame contains information on major sports venues. First, let's
tabulate the status of the venues.

```{r, include=TRUE}
tab(venues, status)
```


Next, we'll tabulate the sites by country, sorting from highest to lowest. We set digits equal to 4 and add a "Total" category.

```{r, include=TRUE}
tab(venues, country, sort=TRUE, total=TRUE, digits=4)
```


Next, let's tabulate the sites by state, sorting from largest number to smallest number of sites. We'll remove all missing observations from the data set, add a total row, and limit the states to the 10 most frequent, plus an "Other" category.

```{r, include=T}
tab(venues, state, sort = TRUE, na.rm = TRUE, total = TRUE, maxcat=10)
```

Finally, let's list the states that have at least 5% of the venues, combining the rest into an "Other" category. 


```{r, include=T}
tab(venues, state,  minp=0.05)
```



